Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-10 paper/main.tex
[issue 2.1] talk about not explicitly designed features

Almost all star-galaxy classifiers published in the literature use
the reduced summary information available from astronomical catalogs.
Constructing catalogs requires careful engineering and considerable domain expertise
to transform the reduced, calibrated pixel values that comprise an image into suitable features,
such as magnitudes or shape information of an object.
In a branch of machine learning called \textit{deep learning},
features are not designed by human experts;
they are learned directly from data by deep neural networks.
Deep learning has been applied successfully to galaxy morphological
classification in Sloan Digital Sky Survey~\citep[SDSS;][]{dieleman2015rotation}
and Cosmic Assembly Near-infrared Deep Extragalactic Legacy
Survey~\citep[CANDELS;][]{huertas2015catalog} and to photometric redshift
estimation~\citep{hoyle2015measuring},
but it has not yet been applied to the problem of source classification.

>>>>

Almost all star-galaxy classifiers published in the literature use
the reduced summary information available from astronomical catalogs.
Constructing catalogs requires careful engineering and considerable domain expertise
to transform the reduced, calibrated pixel values that comprise an image into suitable features,
such as magnitudes or shape information of an object.
\changed{
In a branch of machine learning called \textit{deep learning}~\citep{lecun2015deep},
features are not designed by human experts;
they are learned directly from data by deep neural networks.
Deep learning methods learn multiple levels of features by
transforming the feature at one level into a more abstract feature at a higher
level.
For example, when an array of pixel values is used as input to a deep learning
method, the features in the first layer might represent locations and orientations
of edges.
The second layer could assemble particular arrangements of edges into more
complex shapes, and subsequent layers would detect objects as
combinations of low-level features.
These multiple layers of abstraction progressively amplify aspects of the input
that are important for classification tasks.
}
Deep learning has been applied successfully to galaxy morphological
classification in Sloan Digital Sky Survey~\citep[SDSS;][]{dieleman2015rotation}
and Cosmic Assembly Near-infrared Deep Extragalactic Legacy
Survey~\citep[CANDELS;][]{huertas2015catalog} and to photometric redshift
estimation~\citep{hoyle2015measuring},
but it has not yet been applied to the problem of source classification.
